Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-18 paper/aldebaran.tex
carma psd; fixed citation
text

\citet{Hatzes2015} reported on RV observations of Aldebaran from the coud\'{e}
\'{e}chelle spectrograph of the Th\"{u}ringer Landessternwarte Tautenburg (TLS), the
Tull Spectrograph of the McDonald 2.7 m telescope, and the Bohyunsan Observatory
\'{E}chelle Spectrograph (BOES) spectrograph of the Bohyunsan Optical Astronomy
Observatory (BOAO) spanning the period from 2000.01 to 2013.92.  Combined with earlier observations \citep{hatzes1993}

@@

>>>>

\citet{Hatzes2015} reported on RV observations of Aldebaran from the coud\'{e}
\'{e}chelle spectrograph of the Th\"{u}ringer Landessternwarte Tautenburg (TLS), the
Tull Spectrograph of the McDonald 2.7 m telescope, and the Bohyunsan Observatory
\'{E}chelle Spectrograph (BOES) spectrograph of the Bohyunsan Optical Astronomy
Observatory (BOAO) spanning the period from 2000.01 to 2013.92.  Combined with earlier observations \citep{hatzes1993}, we construct a full time series spanning more than two decades and attempt to fit this with a Keplerian model and a CARMA noise process.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{psd-zoom.pdf}
\caption{CARMA-derived power spectral density from archival and SONG RV observations of Aldebaran, showing the clear peak at around 2\,\muHz. The dark and light shaded regions represent $1\,\sigma$~and $2\,\sigma$ posterior probability contours. }
\label{psd}
\end{figure}
